Stack Safety as a Security Property

### 2020-07-10 main.tex
Quick fix on def. 7.6

      {\em Observable stack confidentiality} is structured like stack
      confidentiality. Let \(\callmap\) be a callmap\apt{should be implicit and is not used anyway}; for each initial
      state \((\mach_0, \pol_0)\) and \(n\)-transition from \(\mpstate{\mach_c}{\pol_c}\)
      to \(\mpstate{\mach_e}{\pol_e}\) in the induced trace
      \(\mpstate{\mach_0}{\pol_0} \hookrightarrow \MPT\), take any
      variation \(\mach_e' \approx_{\mathit{Cof}(\mach_c,n)} \mach_e\). Let
      \(\mpstate{\mach_e}{\pol_e} \hookrightarrow \MPT_{\mathit{call}} ~ | ~
      \ret{\mach_c}\) and \(\mach_e' \hookrightarrow \machT_{\mathit{call}} ~ | ~
      \ret{\mach_c}\). We must have \(\propdef{ObsTraceConf} ~
      \ret{\mach_c} ~ \MPT ~ \machT\).\apt{What is $M$ ??}.

>>>>

      {\em Observable stack confidentiality} is structured like stack
      confidentiality. For each initial
      state \((\mach_0, \pol_0)\) and \(n\)-transition from \(\mpstate{\mach_c}{\pol_c}\)
      to \(\mpstate{\mach_e}{\pol_e}\) in the induced trace
      \(\mpstate{\mach_0}{\pol_0} \hookrightarrow \MPT\), take any
      variation \(\mach_e' \approx_{\mathit{Cof}(\mach_c,n)} \mach_e\). Let
      \(\mpstate{\mach_e}{\pol_e} \hookrightarrow \MPT_{\mathit{call}} ~ | ~
      \ret{\mach_c}\) and \(\mach_e' \hookrightarrow \machT_{\mathit{call}} ~ | ~
      \ret{\mach_c}\). We must have \(\propdef{ObsTraceConf} ~
      \ret{\mach_c} ~ \MPT_{\mathit{call}} ~ \machT_{\mathit{call}}\).\apt{What is $M$ ??}\rb{I think both of these are the call traces, cf. ObservableStackConfPaper in Coq }.
